Evolution of CSMA Protocols for the IEEE 802.11 Standard

### 2013-01-23 paper.tex
working on algorithms
algorithms with end
working on the algorithms
added fair-share
ready to rewrite algorithms

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Evolution of CSMA Protocols of the IEEE 802.11 Standard}

@@

>>>>

%\usepackage[linesnumbered,noend]{algorithm2e}
\usepackage[linesnumbered]{algorithm2e}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Evolution of CSMA Protocols for the IEEE 802.11 Standard}

@@

\begin{algorithm}
  %\tcc{Initialize $b$.}
  $b \leftarrow \mathcal{U}[0,\rm{CW}_{min}-1]$\;
  \While{there is a packet to transmit}{
    %\tcc{Initialize $a$.}
    $a \leftarrow 0$ \;
    \While{$a < A$}{
      %\tcc{First, backoff.}
      \While{$b>0$}{
        wait 1 slot \;
        $b \leftarrow b-1$ \;
      }
      Attempt transmission \;
      \eIf{success}{
        \tcc{Random backoff.}
        $b \leftarrow \mathcal{U}[0,\rm{CW}_{min}-1]$\;
        break \;
      }
      {
        \tcc{Random backoff.}
        $a \leftarrow a+1$ \;
        $b \leftarrow \mathcal{U}[0,\min (\rm{CW}_{min}*2^a,\rm{CW}_{max}) -1]$\;
      }
    }
  }
  \caption{CSMA/CA}
  \label{alg:CSMA_ECA}
\end{algorithm}

\begin{algorithm}
  %\tcc{Initialize $b$.}
  $b \leftarrow \mathcal{U}[0,\rm{CW}_{min}-1]$\;
  \While{there is a packet to transmit}{
    %\tcc{Initialize $a$.}
    $a \leftarrow 0$ \;
    \While{$a < A$}{
      %\tcc{First, backoff.}
      \While{$b>0$}{
        wait 1 slot \;
        $b \leftarrow b-1$ \;
      }
      Attempt transmission \;
      \eIf{success}{
        \tcc{Deterministic backoff.}
        $b \leftarrow \rm{CW}_{min}/2$\;
        break \;
      }
      {
        %\tcc{If transmission fails.}
        $a \leftarrow a+1$ \;
        \tcc{fall to random backoff.}
        $b \leftarrow \mathcal{U}[0,\min (\rm{CW}_{min}*2^a,\rm{CW}_{max}) -1]$\;
      }
    }
  }
  \caption{CSMA/ECA}
  \label{alg:CSMA_ECA}
\end{algorithm}

\begin{algorithm}
  %\tcc{Initialize $b$.}
  $b \leftarrow \mathcal{U}[0,\rm{CW}_{min}-1]$\;
  \tcc{Hysteresis: The backoff stage is reset only when a node joins the contention or the queue is empty.}
  $a \leftarrow 0$ \;
  \While{there is a packet to transmit}{
    %\tcc{Initialize $a$.}
    \While{$a < A$}{
      %\tcc{First, backoff.}
      \While{$b>0$}{
        wait 1 slot \;
        $b \leftarrow b-1$ \;
      }
      Attempt transmission \;
      \eIf{success}{
        \tcc{Deterministic backoff.}
        $b \leftarrow \rm{CW}_{min}/2$\;
        break \;
      }
      {
        %\tcc{If transmission fails.}
        $a \leftarrow a+1$ \;
        \tcc{fall to random backoff.}
        $b \leftarrow \mathcal{U}[0,\min (\rm{CW}_{min}*2^a,\rm{CW}_{max}) -1]$\;
        \If{$a > m$}
        {
          Discard packet \;
          break \;
        }
      }
    }
  }
  \caption{CSMA/ECA with hysteresis}
  \label{alg:CSMA_ECA_hist}
\end{algorithm}

\begin{algorithm}
  %\tcc{Initialize $b$.}
  $b \leftarrow \mathcal{U}[0,\rm{CW}_{min}-1]$\;
  \tcc{Hysteresis: The backoff stage is reset only when a node joins the contention or the queue is empty.}
  $a \leftarrow 0$ \;
  \While{there is a packet to transmit}{
    %\tcc{Initialize $a$.}
    \While{$a < A$}{
      %\tcc{First, backoff.}
      \While{$b>0$}{
        wait 1 slot \;
        $b \leftarrow b-1$ \;
      }
      \tcc{Fair-share: $2^a$ packets are transmitted.}
      Attempt aggregate transmission of $2^a$ packets\;
      \eIf{success}{
        \tcc{Deterministic backoff.}
        $b \leftarrow \rm{CW}_{min}/2$\;
        break \;
      }
      {
        %\tcc{If transmission fails.}
        $a \leftarrow a+1$ \;
        \tcc{fall to random backoff.}
        $b \leftarrow \mathcal{U}[0,\min (\rm{CW}_{min}*2^a,\rm{CW}_{max}) -1]$\;
      }
    }
  }
  \caption{CSMA/ECA with hysteresis and fair-share}
  \label{alg:CSMA_ECA_hist}
\end{algorithm}
